Arc Blanc: a real time ocean simulation framework

### 2024-11-12 paper.tex
Fixed mask calculations
Add missing space in sound equation

While $h_b$ is defined by the user, the value of $w_f$ is estimated as follows:
\begin{equation}
	h_f = \mathbf{v_M}h_{M}\times i_f\times\frac{v_w}{v_{M}},
\end{equation}
where $\mathbf{v_M}$ is the velocity of the body $M$, $h_M$ is the full height of $M$, $i_f$ is a user parameter allowing more user control, $v_w$ is the submerged volume of $M$ (see Section~\ref{sec:fluidToSolidAction}), and $v_{M}$ is the full volume of $M$.
Hence, for more realism $h_f$ is made proportional to the velocity of $M$:
the faster $M$ moves, the bigger the waves generated by $M$ at its front are.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Incompressibility}
As mention in Section~3.3.2 of Hulin \etal (2001) \cite{hulinHydrodynamiquePhysique2001}, a fluid can be considered incompressible if $u<<c_{sound}$ where $c_{sound}$ if the sound speed in ocean which is approximately equal to $c_{sound} = 1530m.s^{-1}$\footnote{see \url{https://en.wikipedia.org/wiki/Sound_speed_profile}.}.
Aside from phenomena such as hurricane, this inequality seems reasonable for oceans, and leads to consider that ocean is incompressible.
More formally:
\begin{equation}
	\rho(t)=\rho.
\end{equation}
Consequently, density can be factorized in each term of equations \ref{equa:ns0}.

>>>>

While $h_b$ is defined by the user, the value of $h_f$ is estimated as follows:
\begin{equation}
	h_f = ||\mathbf{v_M}||h_{M}\times i_f\times\frac{v_w}{v_{M}},
\end{equation}
where $\mathbf{v_M}$ is the velocity of the body $M$, $h_M$ is the full height of $M$, $i_f$ is a user parameter allowing more user control, $v_w$ is the submerged volume of $M$ (see Section~\ref{sec:fluidToSolidAction}), and $v_{M}$ is the full volume of $M$.
Hence, for more realism $h_f$ is made proportional to the velocity of $M$:
the faster $M$ moves, the bigger the waves generated by $M$ at its front are.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Incompressibility}
As mention in Section~3.3.2 of Hulin \etal (2001) \cite{hulinHydrodynamiquePhysique2001}, a fluid can be considered incompressible if $u<<c_{sound}$ where $c_{sound}$ if the sound speed in ocean which is approximately equal to $c_{sound} = 1530~m.s^{-1}$\footnote{see \url{https://en.wikipedia.org/wiki/Sound_speed_profile}.}.
Aside from phenomena such as hurricane, this inequality seems reasonable for oceans, and leads to consider that ocean is incompressible.
More formally:
\begin{equation}
	\rho(t)=\rho.
\end{equation}
Consequently, density can be factorized in each term of equations \ref{equa:ns0}.
